Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-10 paper.tex
chore: minor in the fig 1 description, add manual vs automatic design in the abstract

\begin{abstract}
Coordinatinating a group of intelligent agents in multi-agent systems 
 is a research problem that has been addressed for a long time, 
 due to the challenges posed by distribution and the definition of distributed intelligence. 
%
The problem is even more evident in collective adaptive systems, 
 where the scale of the systems considered makes the definition of collective behaviours even more challenging.

In this paper, we consider a new reinforcement learning approach 
  for the definition of intelligent agents called \emph{Field-Informed reinforcement learning}, 
  where we use computational \emph{computational fields} to manage the interaction between agents 
  and Graph Neural Networks to learn a local behaviour necessary to solve collective tasks. 
%
This allows us to create distributed controllers informed by a collective knowledge 
 distilled during learning but that use only local information at runtime.
% 
We demonstrate the effectiveness of this new approach in a simulated use case 
 where coordination tasks are successfully solved. \lukas{do we really have multiple case studies?} 
\end{abstract}

@@

  \caption{High-level description of Field-Informed reinforcement learning dynamics}

>>>>

\begin{abstract}
Coordinatinating a group of intelligent agents in multi-agent systems 
 is a research problem that has been addressed for a long time, 
 due to the challenges posed by distribution and the definition of distributed intelligence. 
%
The problem is even more evident in collective adaptive systems, 
 where the scale of the systems considered makes the definition of collective behaviours even more challenging. 
% 
Thus far, two main macro approaches have been proposed for creating distributed controllers: 
 \emph{manual design}, in which programmers build the controllers directly, and 
 \emph{automatic design}, which involves synthesizing programs using machine learning methods.
%
In this paper, we consider a new \emph{hybrid} approach called  \emph{Field-Informed reinforcement learning}, 
  where we use computational \emph{computational fields} to manage the interaction between agents 
  and \emph{Graph Neural Networks} to learn a local behaviour necessary to solve collective tasks. 
%
This allows us to create distributed controllers informed by a collective knowledge 
 distilled during learning but that use only local information at runtime.
% 
We demonstrate the effectiveness of this new approach in a simulated use case 
 where coordination tasks are successfully solved. \lukas{do we really have multiple case studies?} 
\end{abstract}

@@

  \caption{High-level description of Field-Informed reinforcement learning dynamics. 
  For each time step, a graph is constructed from the environment, and it will associate each node with a local feature (hexagons in the picture). 
  Using this feature, an aggregate program computes spatio-temporal information that enhances the feature set of each node, depicted as colours in the middle graph. 
  Finally, utilizing the GNN, actions are computed for each node in the system to be performed against the environment, enabling advancement in the simulations according to swarMDP rules.
